The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
Remove duplicate from MC
Effect of extinction

$s$ spread equally from zero (no multiple-birth
event, thus a BD model) to one (species are created only from multiple-birth
events) and three intermediate values of 0.25, 0.5 and 0.75. Aggregating all
components of $s$, we show the effect of $s$ on $e$ in figure \ref{fig:1}.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r c c c}
    \hline
    Symbol                & Expectation & Expected figure & Measured figure \\
    \hline
    \hline
    $\mathcal{H}_1$       & For a higher $s$, $e$ will increase monotonously & \ref{fig:h_1} & \ref{fig:1} \\
    $\mathcal{H}_2$       & Extinction rates have no effect on $e$ & \ref{fig:h_2} & Not yet \\
    $\mathcal{H}_3$       & The timing of multiple-birth events has no effect on $e$ & \ref{fig:h_3} & Not yet \\
    $\mathcal{H}_4$       & An MBD tree will have a higher $e$ than its twin BD counterpart & \ref{fig:h_4} & Not yet \\
    $\mathcal{H}_5$       & The number of taxa has no effect on $e$ & \ref{fig:h_5} & Not yet \\
    $\mathcal{H}_6$       & A higher number of taxa decreases the variance in $e$ & \ref{fig:h_6} & Not yet \\
    $\mathcal{H}_7$       & The MBD regime has no effect on $e$ & \ref{fig:h_7} & Not yet \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:hypotheses}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\item To see the effect of the extinction rate on the relation 
between $s$ and $e$, we simulate phylogenies
with different extinction rates $\mu$. We use values of $\mu$
of 0.0, 0.1 and 0.2. An extinction rate of zero has two features:
(1) the model falls back to a pure multiple-birth model, 
(2) all multiple-birth events are observed.
For the different values of $\mu$, we show
the relation between $s$ and $e$ in figure \ref{fig:2}.

@@

\item We expected the effect of extinction on the relation
between $s$ and $e$ to be neutral (figure \ref{fig:h_2}). 
Figure \ref{fig:2} shows the effect 
measured in this experiment.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_2.png}
  \caption{
    The effect of extinction on the relation between s on e
  }
  \label{fig:2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r c c c}
    \hline
    Symbol                & Expectation & Expected figure & Measured figure \\
    \hline
    \hline
    $\mathcal{H}_1$       & For a higher $s$, $e$ will increase monotonously & \ref{fig:h_1} & \ref{fig:1} \\
    $\mathcal{H}_2$       & Extinction rates have no effect on $e$ & \ref{fig:h_2} & \ref{fig:2} \\
    $\mathcal{H}_3$       & The timing of multiple-birth events has no effect on $e$ & \ref{fig:h_3} & Not yet \\
    $\mathcal{H}_4$       & An MBD tree will have a higher $e$ than its twin BD counterpart & \ref{fig:h_4} & Not yet \\
    $\mathcal{H}_5$       & The number of taxa has no effect on $e$ & \ref{fig:h_5} & \ref{fig:5} \\
    $\mathcal{H}_6$       & A higher number of taxa decreases the variance in $e$ & \ref{fig:h_6} & \ref{fig:6} \\
    $\mathcal{H}_7$       & The MBD regime has no effect on $e$ & \ref{fig:h_7} & Not yet \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:hypotheses}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
